### 2015-06-10 auspice_prev/intro.tex
Initial import of thesis starting from proposal document
Includes all files: tex, pdf, etc.

%!TEX root = Main.tex
\vsp
\section{Introduction}
\label{sec:intro}
``Mobile'' has long arrived, but the Internet remains unmoved. Today, there is roughly one cellphone per human; the number of smartphones sold last year alone roughly equals the number of wired hosts on the Internet \cite{gartner}; and the total traffic originated by mobiles is poised to approach that by wired devices \cite{cisco-vni}. However, the current Internet continues to operate as it did when dominated by tethered hosts, simply ignoring frequent endpoint mobility.

Today, an application developer can not easily initiate communication with a smartphone even when it has a public IP address as there is no global infrastructure support for locating it. Applications like smartphone notification systems, playback video, or cloud storage have to develop application-level support to enable a seamless experience for their users even as they change addresses several times a day, or let connections break (as popular VoIP apps do today).   The lack of intrinsic support for mobility means that developers are forced to redundantly develop and maintain common-case functionality. Furthermore, we are paying an unknowable price in terms of long-term growth and innovation by straitjacketing communication initiation to be unidirectional.

@@

Many before us have criticized the Internet architecture's poor support for mobility as well as multihoming \cite{HIP,LISP,HAIR,MobilityFirst}. A common criticism is the Internet's so-called conflation of identity and location, i.e., the use of an IP address both to represent the identity of an interface as well as its network location, which is problematic for mobility (same identity, changing locations) and multihoming (single identity, multiple locations). It is commonly accepted wisdom that a cleaner separation of identity and location is instrumental to fixing these problems. However, the Internet does separate identities (domain-names) from network locations (IP addresses) through DNS. Most high-level programming languages also provide syntactic sugar to \verb+connect+ to names remaining oblivious to IP addresses; and %name owners can and do employ managed DNS services or CDNs to return the best-positioned network location corresponding to multi-homed names. 
techniques from a long line of work on connection migration could be employed to seamlessly handle mid-connection mobility.

But a key missing element from this package today is a distributed name resolution infrastructure that can scale to orders of magnitude higher update rates than envisioned when DNS was created. To appreciate the envisioned scale, consider tens of billions of mobile identifiers changing network addresses at least tens of times per day. DNS's heavy reliance on TTL-based caching, a key strength recognized by its creators, researchers, and operators alike, poses a significant handicap by increasing update propagation delays, load on name servers, and overall client-perceived latency. It is not uncommon for DNS update propagation to take a day or more, resulting in long  outage times when online services have to be moved unexpectedly, prompting cries for help on operator forums \cite{serverfault,dns-long-update}. A less widely noted limitation of DNS is its reliance on hierarchical names for scaling via federation and its single root of trust, which constrains mobile applications from selecting arbitrary application-specific names (as elaborated in $\S$\ref{sec:whyNotDNS} and $\S$\ref{sec:design_overview}).

@@

Our position is that seamless support for mobility requires a logically centralized global name service that rapidly translates identities to locations irrespective of how exactly identities and locations are individually represented. Our primary contribution is the design, implementation, and evaluation of \auspice, a distributed system that helps address this challenge. Compared to today's ICANN/DNS-based approach, our approach cleanly separates name resolution from adjudication and certification issues ($\S$\ref{sec:design_overview}). \auspice\ is also deployable as a managed DNS provider in today's Internet; compared to them, a key strength of \auspice\ is a {\em demand-aware} replica placement engine that significantly reduces the {\em time-to-connect} to mobile destinations in a cost-effective manner. Under light load, \auspice's demand-aware replica placement aggressively uses available resources to massively replicate name records, while under heavy load, it carefully controls the number and choice of replica locations based on the read-write patterns and pockets of high demand for each name.

%low lookup latency, low update cost, and high availability.  \auspice\ achieves low-latency by inferring pockets of high demand for a name so as to create replicas of  for that name close to them. \auspice\ achieves low latency,  low update cost,  and high availability using a placement optimization algorithm that (1) controls the number of replicas based on the observed read and write rates, and (2) determines where to place replicas based both on the inferred pockets of demand and the aggregate load at node locations near those pockets.

We have implemented a prototype of \auspice\ as a geo-distributed key-value store to serve as a flexible name resolution service for the current Internet as well as several ``future'' Internet or endpoint architectures such as MobilityFirst\cite{MobilityFirst}, HIP\cite{HIP}, or XIA\cite{XIA}. We have extensively evaluated \auspice\  using a combination of Planetlab, emulation clusters, and Amazon EC2.  Our contributions are as follows.
\begin{enumerate}
\item A case for a global name service as an indispensable part of any Internetwork design with intrinsic support for high mobility ($\S$\ref{sec:case}).
\vsp
\item \auspice, a scalable, geo-distributed, federated global name service that significantly reduces the time-to-connect under any given resource constraints despite high mobility and arbitrary endpoint identifiers ($\S$\ref{sec:design},$\S$\ref{sec:eval}). 
\figvsp
\item A proof-of-concept demonstration of intrinsic support for---{\em(i)} all four types of endpoint mobility; {\em(ii)} novel context-aware delivery primitives that generalize name- or address-based communication---over the current Internet as well as MobilityFirst \cite{MobilityFirst} ($\S$\ref{sec:e2e}). 
\vsp
\item Comparison against several best-of-breed managed DNS services showing that \auspice's  demand-aware approach significantly lowers time-to-connect and/or update cost even for today's (hardly mobile) domain names ($\S$\ref{sec:managed}).
\vsp
\end{enumerate}
\vsp

To provide a historical perspective, until the early 80s, the Internet relied on a system called \verb+HOSTS.TXT+ for name resolution, which was simply a centrally maintained text file distributed to all hosts. The current Internet's distributed DNS  arose in response to the rapidly increasing file size and distribution costs. Mockapetris and Dunlap \cite{DNS} point to TTL-based caching to reduce load and response times as a key strength, noting that ``{\em{the XEROX system {\em [Grapevine \cite{grapevine}]} was then ... the most sophisticated name service in existence, but it was not clear that its heavy use of replication, light use of caching ... were appropriate}}''. We have since come a full circle, turning to  active replication ($\S$\ref{sec:whyNotDNS}) in \auspice\ in order to address the challenges of mobility, a concern that wasn't particularly pressing  in the 80s. Compared to classical systems like Grapevine or ClearingHouse, \auspice\ enables support for automated {\em demand-aware} replica placement for {\em arbitrary names} (using several modern design elements such as consensus, the key-value abstraction, self-certifying names, consistent hashing, etc).  \auspice, through its support for context-aware delivery, is also a step towards addressing some of the challenges to which Lampson alludes on representing ``descriptive names" \cite{Lampson}.

>>>>

\chapter{A Global Name Service for a Highly Mobile Internet}
\label{ch:auspice}
\vsp
\section{Introduction}
\vsp

``Mobile'' has long arrived, but the Internet remains unmoved. Today, there are almost 6 billion cellphones, over a billion of which are smartphones \cite{gartner}. The number of smartphones alone now exceeds the number of tethered hosts on the Internet, and recent studies \cite{cisco} suggests that the total data traffic generated by mobiles now exceeds that of tethered clients. However, the current Internet continues to operate as it did when dominated by tethered hosts, simply ignoring frequent endpoint mobility.

Today, one can not easily initiate communication with a smartphone (even when it has a public IP address) as there is no global infrastructure support for locating it. Applications like Netflix, Dropbox, or smartphone notification systems have to develop application-level support to enable a seamless experience for their users even as they change addresses several times a day, or let connections break (as popular VoIP apps do today).   The lack of intrinsic support for mobility means that developers are forced to redundantly develop and maintain common-case functionality. We are also paying an unknowable price in terms of long-term growth and innovation by forcing communication initiation to be unidirectional.

@@

Many before us have criticized the Internet architecture's poor support for mobility as well as multihoming \cite{HIP,LISP,HAIR,MobilityFirst}. A common criticism is the Internet's so-called conflation of identity and location, i.e., the use of an IP address both to represent the identity of an interface as well as its network location, which is problematic for mobility (same identity, changing locations) and multihoming (single identity, multiple locations). It is commonly accepted wisdom that a cleaner separation of identity and location is instrumental to fixing these problems. However, the Internet does separate identities (domain-names) from network locations (IP addresses) through DNS. Most high-level programming languages also provide syntactic sugar to ``connect'' to names remaining oblivious to IP addresses; and %name owners can and do employ managed DNS services or CDNs to return the best-positioned network location corresponding to multi-homed names. 
techniques from a long line of work on connection migration can be employed to seamlessly handle mid-connection mobility.

But a key missing element from this package today is a distributed resolution infrastructure that can scale to orders of magnitude higher update rates than envisioned when DNS was created. To appreciate our envisioned scale, consider 10 billion mobile identifiers moving across a 100 different networks per day (or an aggregate rate of roughly 1M/sec). DNS's heavy reliance on TTL-based caching, a key strength recognized by its creators, researchers, and operators alike, also poses a significant handicap by increasing update propagation delays. It is not uncommon for DNS update propagation to take a day or more, resulting in long  outage times when online services have to be moved unexpectedly, prompting cries for help on operator forums \cite{serverfault}.

@@

Our position is that seamless support for mobility requires a global name service that rapidly translates identities to locations irrespective of how exactly identities and locations are individually represented. %In $\S$\ref{sec:bg}, we present a design space exploration comparing a number of classic and recent alternative architectures to argue that they all need or can significantly benefit from such a global name service to address the challenges posed by high mobility.
Our primary contribution is the design, implementation, and evaluation of \auspice, a distributed system that addresses this challenge. The key strength of \auspice\ is an placement engine  for replicating name records to achieve low lookup latency, low update cost, and high availability.  \auspice\ achieves low-latency by inferring pockets of high demand for a name so as to create replicas of resolvers for that name close to them. \auspice\ achieves low latency,  low update cost,  and high availability using a placement optimization algorithm that (1) controls the number of replicas based on the observed read and write rates, and (2) determines where to place replicas based both on the inferred pockets of demand and the aggregate load at node locations near those pockets.

%As a proof of concept, we have also developed an accompanying user-level mobile socket library that allows endpoints to seamlessly migrate TCP connections.
We have implemented a prototype of \auspice\ as a geo-distributed key-value store to serve as a flexible name resolution infrastructure for the Internet as well as future Internet architecture proposals. We have deployed and evaluated it on several different platforms including Planetlab, a local cluster, and Amazon EC2.  Our contributions are as follows.
\begin{itemize}
\item A case for a global name resolution as an indispensable part of an Internetwork with intrinsic support for mobility.
\item \auspice, a massively scalable, geo-distributed, federatable global name service that significantly reduces the time-to-connect under resource constraints. 
%\auspice\ achieves lookup latencies comparable to leading managed DNS providers with only one-third as many replica locations, and provides a median update latency that is 1.0 s to 24.7 s lower.
%\item Proof-of-concept validation of end-to-end mobility and novel case-study apps leveraging \auspice's support for context-aware communication that generalizes address- or name-based communication. 
\item Evaluation against several leading commercial managed DNS services showing that \auspice\ achieves significantly lower time-to-connect and/or update cost in comparison.
%\emph{Mid-session mobility:} MSocket library enables seamless end-user mobility by migrating a TCP connection from Wi-Fi to 4G in three round trip times.
\end{itemize}

\eat{
\begin{itemize}
\item
\emph{Low response time:} Locality-aware placement helps \auspice\ achieve 5$\times$ lower median lookup latency than a DHT-based replication scheme.
\item
\emph{Capacity:} \auspice\  sustains  a maximum load that is 18$\times$ the maximum load sustained by a replicate-everywhere scheme, and is comparable to the maximum load sustained by DHT-based designs.
\item
\emph{Comparison to managed DNS:} \auspice\ achieves  DNS lookup latencies comparable to a leading managed DNS provider today even with only one third the locations of name resolvers. Median address update latencies for \auspice\  are 100 ms, 2 sec, and 30 sec lower than three managed DNS providers today.
\item
\emph{Support for mid-session mobility:} Fast address updates in \auspice\ enable seamless end-user mobility with connection reestablishments within a few hundred milliseconds.
\end{itemize}
}

### 2015-06-10 auspice_prev/related.tex
Initial import of thesis starting from proposal document
Includes all files: tex, pdf, etc.

%\section{Limitations and future work}
%\vspace{-0.1in}
%\subsection{Limitations and future work}

@@

\textbf{Paxos overhead:}
}
\vspace{-0.1in}
\section{Related work}
\label{sec:related}

@@

Our work draws on lessons learned from an enormous body of prior work on distributed systems as discussed below.

%Compared to the former, the novel contribution in \auspice\ is an engine to {automate} geo-distributed replica placement to achieve low-latency, low-cost, and high availability.  Compared to the latter, our contribution is a global name service with intrinsic support for mobility for the Internet as well as ``future'' Internet or endpoint architectures such as MobilityFirst, XIA, or HIP.
%in a low-cost, locality- and load-aware manner.

%\textbf{DNS:} Until the early 80s, the Internet relied on a system called \verb+HOSTS.TXT+ for name resolution, which was simply a centrally maintained text file distributed to all hosts. The current Internet's distributed DNS \cite{DNS} arose in response to the rapidly increasing size of the file and the cost of distributing it. Mockapetris and Dunlap point to TTL-based caching to reduce load and response times as a key strength, noting that ``{\em the XEROX system {\em [Grapevine \cite{grapevine}]} was then ... the most sophisticated name service in existence, but it was not clear that its heavy use of replication, light use of caching ... were appropriate}''. We have since come a full circle, turning to  active replication in \auspice\ in order to address the challenges of mobility, a concern that wasn't particularly pressing  in the 80s. Compared to classical systems like Grapevine or ClearingHouse, \auspice\ enables support for automated demand-aware replica placement for arbitrary names; it also differs in several basic elements such as the use of Paxos, the key-value abstraction, self-certifying names, consistent hashing etc., that were not known back then.  \auspice, through its support for context-aware delivery, is also a step towards addressing some of the challenges to which Lampson alludes on representing ``descriptive names" \cite{Lampson}.

%\textbf{DNS enhancements:} 
%Since then, 
{\bf{DNS.}} Many have studied issues related to performance, scalability, load balancing, or denial-of-service vulnerabilities in DNS's resolution infrastructure \cite{Pappas,codons-paper,Brownlee,dnssec}. Several DHT-based alternatives have been put forward \cite{codons-paper,cox,DHTdns} and we compare against one representative proposal, Codons \cite{codons-paper}. In general, DHT-based designs are ideal for balancing load across servers, but are less well-suited to scenarios with a large number of service replicas that have to coordinate upon updates, and are at odds with scenarios requiring placement of replicas close to pocket of demand. In comparison, \auspice\ uses a planned placement approach.

Vu et al. describe DMap \cite{VuICDCS12}, an in-network DHT scheme 
that is similar in spirit to \staticthree\ as evaluated in our experiments ($\S$\ref{sec:eval}) (with a more direct comparison in \cite{techreport}), showing that demand-aware placement can dramatically outperform randomized placement.

@@

\textbf{Server selection.} Many prior systems have addressed the server selection problem with data or services replicated across a wide-area network. Examples include anycast services \cite{oasis,Bhattacharjee:1997:AA:839292.843045,donar} to map users to the best server based on server load or network path characteristics. These systems as well as CDNs and cloud hosting providers %\cite{AWS-load-balancing} 
share our goals of proximate server selection and load balance given a fixed placement of server replicas. \auspice\ differs in that it additionally considers replica placement itself as a degree of freedom in achieving latency or load balance.

\textbf{Dynamic placement.} We were unable to find prior systems that {\em automatically} reconfigure the {\em geo-distributed} replica locations of frequently {\em mutable objects} while preserving {\em consistency} (i.e., those satisfying all four italicized properties). However, reconfigurable placement has been studied for static or slow changing content \cite{gwertzman:95b} or within a single datacenter, or without replication. For example, Volley \cite{volley} optimizes the placement of mutable data objects based on the geo-distribution of accesses and is similar in spirit to \auspice\ in this respect, however it implicitly assumes a single replica for each object, so it does not have to worry about high update rates or replica coordination overhead. %As shown in  $\S$\ref{sec:eval}, creating multiple replicas of objects or services can significantly reduce user-perceived response times while also enhancing opportunities to balance load provided update cost is taken into account.
%\auspice\ is also similar in spirit to edge services hosted by CDNs. However, unlike \auspice, the geo-distributed locations of edge services as well as cloud-hosted services today are chosen manually and infrequently updated. %In comparison, \auspice\ automates geo-distributed placement of replicas, but the ``service'', a key-value store, is much simpler compared to black-box cloud-hosted services.

@@

\auspice\ is related to many distributed key-value stores \cite{mongodb,Escriva,cassandra}, most of which are optimized for distribution within, not across, data centers. Some (e.g., Cassandra) support a geo-distributed deployment using a fixed number of replica sites. Spanner \cite{spanner} is a geo-distributed data store that synchronously replicates data (``directories'') across datacenters with a semi-relational database abstraction. Compared to Spanner, \auspice\ does not provide any guarantees on operations spanning multiple records, but unlike Spanner's geographic placement of replicas that  ``administrators control'' by creating a ``menu of named options'',  \auspice\  automatically reconfigures the number and placement of replicas so as to reduce lookup latency and update cost. Furthermore, Spanner assigns a large number of directory objects to a much smaller number of fixed Paxos groups; \auspice\ supports an arbitrarily reconfigurable Paxos group per object based on principles in recent theoretical work on reconfigurable consensus, e.g., Vertical Paxos \cite{vertical-paxos} and the more recent report on Viewstamped Replication Revisited \cite{liskov12vr}.

@@

>>>>

%!TEX root = New.tex
%\section{Limitations and future work}
%\vspace{-0.1in}
%\subsection{Limitations and future work}

@@

\textbf{Paxos overhead:}
}
\vspace{-0.1in}
\section{Related Work}
\label{sec:related}

@@

Our work on \auspice\ draws on lessons learned from an enormous body of prior work on distributed systems for name resolution as well as broader network architectural efforts. Compared to the former, the novel contribution in \auspice\ is an engine to {automate} geo-distributed replica placement to achieve low-latency, low-cost, and high availability.  Compared to the latter, our contribution is a name service that enables intrinsic support for mobility for several ``future'' Internet architectures such as HIP, MobilityFirst, and XIA.
%in a low-cost, locality- and load-aware manner.

\textbf{DNS:} Until the early 80s, the Internet relied on a system called HOSTS.TXT for name resolution, which was simply a centrally maintained text file distributed to all hosts. The current Internet's distributed DNS \cite{DNS} arose in response to the rapidly increasing size of the file and the cost of distributing it. Mockapetris and Dunlap point to TTL caching to reduce load and response times as a key strength, noting that ``the XEROX system (Grapevine \cite{grapevine}) was then ... the most sophisticated name service in existence, but it was not clear that its heavy use of replication, light use of caching ... were appropriate''. We have since come a full circle, turning to  full replication in \auspice\ in order to address the challenges of mobility, a concern that wasn't particularly pressing  in the 80s. Compared to systems like Grapevine or ClearingHouse, \auspice\ enable support for dynamic, automated placement of replicas and addresses some of the challenges described by Lampson on representing ``descriptive names" \cite{Lampson}.

%\textbf{DNS enhancements:} 
Since then, many have studied issues related to performance, scalability, load balancing, or denial-of-service vulnerabilities in DNS's resolution infrastructure \cite{Pappas,codons-paper,Brownlee,dnssec}. Several DHT-based alternatives have been put forward \cite{codons-paper,cox,beehive,DHTdns} and we compare against a representative proposal, Codons \cite{codons-paper}. In general, DHT-based designs are ideal for balancing load across servers, but are less well-suited to scenarios with a large number of service replicas that have to coordinate upon updates, and are at odds with scenarios requiring placement of replicas close to pocket of demand. In comparison, \auspice\ uses planned placement approach.

@@

\textbf{Server selection:} A number of prior systems have addressed the server selection problem where data or services are replicated across a wide-area network. OASIS \cite{oasis} maps users based on IP addresses to the best server based on latency and server load. DONAR \cite{donar} enables an expressive API for content providers to specify performance or cost optimization objectives under load balance constraints. These systems as well as CDNs and cloud hosting providers \cite{AWS-load-balancing} share our goals of proximate server selection and load balance given a fixed placement of server replicas. \auspice\ differs in that it additionally considers replica placement itself as a degree of freedom in achieving latency or load balance.

\textbf{Placement:} %Existing systems that dynamically make replica placement decisions based on observed demand patterns can be classified as {\em static content} or {\em service} placement systems. In general, the latter addresses a more complex problem than the former as static content can be cached easily obviating sophisticated content placement strategies \cite{DoWeNeedReplica}. In this parlance, \auspice\ is an instantiation of a service placement system where the service is name resolution.
 %Nevertheless, static content placement decisions can have a nontrivial impact on network load or cost concerns \cite{ATTVoD,SharmaInfocom09,NCDN}. 
Volley \cite{volley} optimizes the placement of dynamic data objects based on the geographic distribution of accesses to the object and is similar in spirit to \auspice\ in that respect. However, Volley implicitly assumes a single replica for each object and therefore does not have to worry about high update rates or coordination overhead for replica consistency. %As shown in  $\S$\ref{sec:eval}, creating multiple replicas of objects or services can significantly reduce user-perceived response times while also enhancing opportunities to balance load provided update cost is taken into account.
\auspice\ is also similar in spirit to edge services offered by commercial CDNs. However, unlike \auspice, the geo-distributed locations of edge services as well as cloud-hosted services today are chosen manually and infrequently updated. %In comparison, \auspice\ automates geo-distributed placement of replicas, but the ``service'', a key-value store, is much simpler compared to black-box cloud-hosted services.

@@

\textbf{Data stores:} \auspice\ is also related to many distributed key-value stores \cite{mongodb,Escriva,Lloyd,cassandra}, but most of these are optimized for distribution within, not across data centers. Some like Cassandra \cite{cassandra} support a geo-distributed deployment (but are rarely used in this mode) using a fixed number of replica sites. Spanner \cite{spanner} is a geo-distributed data store that synchronously replicates data across datacenters and provides  database like abstractions e.g., distributed transactions, semi-relational data model. \auspice\ does not provide any guarantees on operations spanning multiple records. In comparison to these systems, \auspice\  automatically determines the number and placement of replicas so as to reduce lookup latency and update cost.

@@

%Vu et al.\cite{VuICDCS12} describe a network-layer-DHT approach to map each self-certifying identifier to a fixed number of resolver locations using different consistent hash functions with clients choosing the closest mapped resolver. This approach is similar in spirit to Static-K as evaluated in our experiments ($\S$\ref{sec:eval}). Our results show that placing name record replicas based on geo-distribution of demand can significantly outperform random placement.
